% LaTeX file for resume 
% This file uses the resume document class (res.cls)

\documentclass[margin]{res} 
% the margin option causes section titles to appear to the left of body text 
\textwidth=5.7in % increase textwidth to get smaller right margin
\textheight=9.4in
\topmargin=-0.3in
\oddsidemargin -.25in
\evensidemargin -.5in
\parsep 10pt
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead[HL]{ }
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[FC]{\it Will now or in the near future will require visa sponsorship.}

\begin{document} 

\name{AASHISH THITE\\[12pt]} % the \\[12pt] adds a blank line after name
 

\address{aashish.thite4189@gmail.com\\www.linkedin.com/in/aashishthite\\https://github.com/aashishthite‎}
\address{\hfill 7800 El Camino Real, Apt\#1125 \\ \hfill Colma, CA-94014, USA\\ \hfill (408) 601-9349}


\begin{resume} 
 
% \section{Objective} 
% Seeking a full-time position in software application development.% focused on Computer Vision, Computer Graphics and Machine Learning.

\section{Education} 
{\bf University of Wisconsin-Madison} \\
M.S. Electrical Engineering (GPA: 3.75/4) \hfill {\it May 2014} \\
%Received full tuition scholarship with Research Assistantship \\
\\
{\bf Vishwakarma Institute of Technology-Pune} \\
B.E. in Electronics and Telecommunications Engineering (GPA: 8.77/10) \hfill {\it May 2011}

\section{Skills}
Strong Math background, C++ (proficient), Java (proficient), C (competent), Python(competent), Go(competent), CUDA, OpenGL, UNIX/Linux.

\section{Coursework}
Algorithms, Computer Vision, Machine Learning, Computer Graphics, 
%Computational Cognitive Sciences, 
Operating Systems, Statistical Estimation Theory, Advanced Image Processing, Data Structures.

\section{Experience}
 {\bf Twitch} \\
 Software Engineer, Video Team\hfill {\it July 2014 - present}
 
 {\bf University of Wisconsin-Madison} \\
Teaching Assistant,  Dept. of Computer Sciences\hfill {\it Jan 2014 - May 2014}
\begin{itemize} \itemsep -2pt  % reduce space between items
 \item Course: CS760 Machine Learning
\end{itemize}

Research Assistant(Computer Vision), Dept. of Computer Sciences \hfill {\it May 2013 - May 2014}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Designed a novel algorithm for denoising images using multiple views.
 \item Used CUDA C to give this highly parallel algorithm a 4 times speed-up. 
 \end{itemize}


  %{\bf University of Wisconsin-Madison,} Dept. of Botany \\
Project Assistant,  Dept. of Botany\hfill {\it Sept 2012 - Aug 2013}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Developed HypoTrack, a MATLAB tool for tracking texture on hypocotyls for analysis of plant growth. The tool is published on iPlant Collaborative to for botanists world-wide who study plant growth.
 \end{itemize}
  {\bf Scicom Software India Pvt. Ltd.} \\
Project Intern\hfill{\it Aug 2011 - July 2012}
 \begin{itemize} \itemsep -2pt  % reduce space between items
 \item Designed and developed a simulator software for a control system using C\#. This reduced the time-to-market by 33\% and earned a new project for the organization.
 \item Worked with a team in design of hardware for the control system. Reduced product cost by 25\% of the budget. Followed German safety standards. 

 \end{itemize}
\section{Projects}
{\it Real-time 3D Reconstruction using Kinect:} Performed bilateral filtering on depth map. Rendered implicit surfaces using Signed Distance Function. {\it(OpenCL, GPU, C\#, Kinect)}
\\{\it MoshBall:} Developed a 3D game. Developed physics simulation, I/O interaction and background rendering for the game. {\it (C++, OpenGL, GLSL, Box2D)}  
\\{\it Music Recommendation System:} Recommended top ten songs to a user using offline collaborative filtering, normalized conditional probabilities and k-NN on the listening history of users. {\it (Java, MySQL)}

\section{Side Projects}
HDR Image Fusion, Photo-metric Stereo, Panoramic Image Stitching, Othello.
\section{Co-Curricular}
\begin{itemize} \itemsep -2pt  % reduce space between items
 \item Participated in UW-HuB Hackathon; designed and developed a 2D game in Java.
 \item Winner(1st place) - Codility Coding Challenge. Participant- Hacker Olympics by HackerRank.
 \end{itemize}

 %\section{References}
%Available on request.


\end{resume} 


\end{document} 
